Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-05 doc/sc2012/soop.tex
punctuation

To dynamically detect and enforce data dependences,
the SOOP considers, for each task $t$, the
the regions $t$ uses and ensures $t$ waits on any
earlier task whose region uses conflict with $t$'s.  There is a
difficulty, however.  The programmer's regions are logical; a region
names a set of objects, but does not say where those objects
are in memory.  To ensure dependences are satisfied the SOOP must also {\em map} $t$: assign an
appropriate physical instance to each of $t$'s logical regions.  Thus, dependence
analysis requires knowing both which tasks $t$ depends on and how those
other tasks are mapped.

@@

Detecting mapping dependences between a newly registered task $t$ and
a previously registered task $t'$ requires comparing the two sets of
logical regions accessed.  For each logical region used by $t'$ that
may {\em alias} (may share data with) a logical region used by $t$, the privileges and
coherence modes are compared to determine whether a dependence exists.
If both regions need only read privileges there is never a dependence,
but if either task needs write or reduction privileges, the coherence
modes are compared using the table in Figure~\ref{fig:dependence}.
{\tt Dep} indicates dependence while {\tt None}
indicates independence.  {\tt Same} is a dependence unless the two tasks
use the same physical instance of the logical region.  Since tasks
haven't mapped physical instances at this point in the pipeline {\tt Same} is always
a mapping dependence.
%\footnote{For example, if two tasks wish to acess the region with atomic coherence, then if they are working on the same physical copy of the data atomicity can be guaranteed using, e.g., locking.  If they are working on different copies of the data then the only safe execution strategy for Legion is to serialize the two tasks.}
{\tt Cont} 
indicates a dependence contingent on whether it is a reader or
writer that is Atomic (e.g. Atomic Read-Write and Simultaneous
Read-Only will not cause a dependence).

>>>>

To dynamically detect and enforce data dependences,
the SOOP considers, for each task $t$, the
regions $t$ uses and ensures $t$ waits on any
earlier task whose region uses conflict with $t$'s.  There is a
difficulty, however.  The programmer's regions are logical; a region
names a set of objects, but does not say where those objects
are in memory.  To ensure dependences are satisfied the SOOP must also {\em map} $t$: assign an
appropriate physical instance to each of $t$'s logical regions.  Thus, dependence
analysis requires knowing both which tasks $t$ depends on and how those
other tasks are mapped.

@@

Detecting mapping dependences between a newly registered task $t$ and
a previously registered task $t'$ requires comparing the two sets of
logical regions accessed.  For each logical region used by $t'$ that
may {\em alias} (may share data with) a logical region used by $t$, the privileges and
coherence modes are compared to determine whether a dependence exists.
If both regions need only read privileges there is never a dependence,
but if either task needs write or reduction privileges, the coherence
modes are compared using the table in Figure~\ref{fig:dependence}.
{\tt Dep} indicates dependence while {\tt None}
indicates independence.  {\tt Same} is a dependence unless the two tasks
use the same physical instance of the logical region.  Since tasks
haven't mapped physical instances at this point in the pipeline,
{\tt Same} is always a mapping dependence.
%\footnote{For example, if two tasks wish to acess the region with atomic coherence, then if they are working on the same physical copy of the data atomicity can be guaranteed using, e.g., locking.  If they are working on different copies of the data then the only safe execution strategy for Legion is to serialize the two tasks.}
{\tt Cont} 
indicates a dependence contingent on whether it is a reader or
writer that is Atomic (e.g. Atomic Read-Write and Simultaneous
Read-Only will not cause a dependence).
